## Setup

First, we need to load some packages. Click the play button to run the code in the block below (remember, you only need to do this once per session).

```{r}
library(tidyverse)
library(openintro)
```

## Q1: Describing categorical data

Let's look at the `employment` variable of the `acs12` data set. In the chunk below, write some code to determine the response options for this variable.

```{r}

```

How many people are in each category? How many missing values are there?

```{r}

```

Create a table that shows the number of people of each gender in each employment category. Does it look like gender and employment status are related?

```{r}

```

## Q2: Describing numeric data

Now let's look at the `hrs_work` variable (the number of hours respondents work in a week)

What is the mean of this variable? What is the median?

```{r}

```

What is the standard deviation?

```{r}

```

What proportion of people in the data set are missing information (have NAs) for this variable?

```{r}

```

## Submission

When you are done, commit your changes and push them to GitHub! ([instructions](https://soc333-sum23.github.io/computing-clonerepo.html))
